\Large \bf \Toolname: Precise False Sharing Detection for COTS Binaries

### 2014-11-06 HotOS'15/paper.tex
Minor typo fixes.

\item It describes a two new, data-centric sampling approaches: \begin{inparaenum}[i)]
\item uniform heap sampling, and
\item selective heap sampling.
\end{inparaenum} Uniform heap sampling enables \Toolname{} to sample objects in the heap uniformly
according to their type. This is beneficial because it improves coverage: if 90\% of false sharing occurs because
of accesses to only 10\% of the data, then \Toolname{} will not miss those races by blindly focusing on the
other 90\% of data. Once data of interesting has been narrowed down, \Toolname{} can apply selective heap
sampling, which focuses sampling on specific types of objects or data accessed by specific code (or both).
\end{itemize}

>>>>

\item It describes two new, data-centric sampling approaches: uniform heap sampling, and selective heap
sampling. Uniform heap sampling enables \Toolname{} to sample objects in the heap uniformly according to
their type. This is beneficial because it improves coverage: if 90\% of false sharing occurs because of accesses
to only 10\% of the data, then \Toolname{} will not miss those races by blindly focusing on the other 90\% of data.
Once data of interesting has been narrowed down, \Toolname{} can apply selective heap sampling, which
focuses sampling on specific types of objects or data accessed by specific code (or both).
\end{itemize}
